signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-18 paper.tex
commit before dinner

The best and the worst encoding share some similarities. In both cases Group 1 tends to contain polar amino acids typical with the average size of residuals. In the best encoding, all charged amino acids, both acids and even weak bases as histidine, also belong to this group. This group, nearly absent in h-region, provides very good distinction between parts of signal peptide for best encoding. In the worst encoding, where polar and charged character of the Group 1 is not that explicit, the difference in frequency between regions is also less visible.

@@

>>>>

\subsection*{Comparision of encodings}

We examined more deeply encodings with the best and the worst sensitivity. In both cases Group 1 tends to contain polar amino acids typical with the average size of residuals. In the best encoding, all charged amino acids, both acids and even weak bases as histidine, also belong to this group. This group, nearly absent in h-region, provides very good distinction between parts of signal peptide for best encoding. In the worst encoding, where polar and charged character of the Group 1 is not that explicit, the difference in frequency between regions is also less visible.

@@

The first set of predictive rules derived by our method lies in the encoding of amino acids. Aside from a confirmation of the accepted signal peptide model (hydrophibicity of the h-region, polarity of the n-region), we also found new relationships. We found the alanine is one of the most typical amino acids for the c-region and occurs there far more often than in the other parts of signal peptides and mature proteins. The presence of alanine in the signal peptide cleavage site~\cite{1986vonheijnea} cannot explain such overrepresentation of group containing alanine in the c-region.
